---
title: "Display data from geoserver in R"
description: "Just a little code snippets."
date: "2024-11-13"
categories: ["coding"]
---


```{r}
library(leaflet)
library(leaflet.extras2)
```

Let's generate a base map:

```{r}
m <-
  leaflet() |>
  addTiles() |>
  setView(-19, 65, zoom = 5)
```

Within R one can easily get a map up via, here taking data from the "old" hafro-geoserver:

```{r}
m |>
   addWMSTiles(baseUrl = "https://gis.hafogvatn.is/geoserver/hafro/wms",
              layers = "hafro:trawl_3857_byte",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       tiled = TRUE,
                                       opacity = 1))
```

On the same geoserver we have (note now in "test"):

```{r}
m |>
   addWMSTiles(baseUrl = "https://gis.hafogvatn.is/geoserver/hafro/wms",
              layers = "test:trawl_3857_byte",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       tiled = TRUE,
                                       opacity = 1))
```


On the same geoserver we also have a trial that does not work:

```{r}
m |>
   addWMSTiles(baseUrl = "https://gis.hafogvatn.is/geoserver/hafro/wms",
              layers = "test:effort06_na_trial",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       tiled = TRUE,
                                       opacity = 1))
```

Now unfortunately, because one has to use point-and-mouse-click when populating geoserver it is unknown why the above does not work.

Rather than trying a raster lets try a simple line:

```{r}
m |>
   addWMSTiles(baseUrl = "https://gis.hafogvatn.is/geoserver/hafro/wms",
              layers = "log:grunnlinur_1979-0041",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       tiled = TRUE,
                                       opacity = 1))
```


Strange brew. If we just do something analogous taking data from the LMÍ geoserver:

```{r}
m |>
  addWMSTiles(baseUrl = "https://gis.lmi.is/geoserver/wms",
              layers = "LHG:landhelgi_12_milur_lina",
              group = "12 mílur",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       #crs = "EPSG:3857",
                                       tiled = TRUE,
                                       opacity = 1))
```

..., solution pending


```{r}
m |> 
  addWMSTiles(baseUrl = "https://hafsja-geoserver.dev.hafogvatn.cloud/geoserver/wms",
              layers = "test:adlaeg-belti_1979-0041",
              group = "12 mílur",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       #crs = "EPSG:3857",
                                       tiled = TRUE,
                                       opacity = 1))



m |> 
  addWMSTiles(baseUrl = "https://hafsja-geoserver.dev.hafogvatn.cloud/geoserver/wms",
              layers = "log:adlaeg-belti_1979-0041",
              group = "12 mílur",
              options = WMSTileOptions(format = "image/png",
                                       transparent  = TRUE,
                                       #crs = "EPSG:3857",
                                       tiled = TRUE,
                                       opacity = 1))



```

